Functional pant indicators - wetland, indicator documentation

### 2023-05-05 functional_plant_indicators_wetland.Rmd
Add functional plant indicators to the book

# Functional plant indicators - wetland {#Functional-plant-indicators-wetland}
# Functional plant indicators (Moisture, Light, pH, Nitrogen)

@@

```{r, echo=F}
Ecosystem <- "våtmark"
Egenskap  <- c("Primærproduksjon","Abiotiske forhold")
ECT       <- "Functional state characteristic"
Contact   <- "Joachim Töpper"
```

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

>>>>

# Functional plant indicators (Moisture, Light, pH, Nitrogen) {#Functional-plant-indicators-wetland}

@@

```{r, echo=FALSE}
Ecosystem <- "våtmark"
Egenskap  <- c("Primærproduksjon","Abiotiske forhold")
ECT       <- "Functional state characteristic"
Contact   <- "Joachim Töpper"
```

```{r, echo=FALSE}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```
